Transactional Memory Concurrency Verification with Landslide

### 2018-03-15 htm/paper.tex
move the variants tables so latex lays em out nicely
mark the winner in bugperf

			& 2,1	&\cpu{  45.78}&\wtm{9.70}&\ints{21}& \cpu{9.47}& \wtm{6.40}& \ints{21	}& \ETA{213} \\

@@

			& 2,2	&\cpu{  84.14}&\wtm{13.59}&\ints{33}& \cpu{10.39}& \wtm{7.70}& \ints{49	}& \ETA{1536} \\
			& 2,3	&\cpu{ 131.91}&\wtm{20.44}&\ints{73}& \cpu{12.83}& \wtm{9.67}& \ints{113	}& \ETA{10752} \\
			& 2,4	&\cpu{ 255.75}&\wtm{37.56}&\ints{257}& \cpu{18.63}& \wtm{15.86}& \ints{257	}& \ETA{73728} \\

@@

			& 3,1	&\cpu{ 114.06}&\wtm{17.45}&\ints{15}& \cpu{9.50}& \wtm{6.79}& \ints{21	}& \ETA{13653} \\
			& 3,2	&\cpu{ 109.60}&\wtm{26.16}&\ints{49}& \cpu{10.72}& \wtm{7.97}& \ints{49	}& \ETA{393216} \\
			& 3,3	&\cpu{ 124.80}&\wtm{20.40}&\ints{73}& \cpu{13.84}& \wtm{11.01}& \ints{113	}& \ETA{11010048} \\
			& 3,4	&\cpu{ 227.49}&\wtm{35.15}&\ints{161}& \cpu{31.37}& \wtm{28.53}& \ints{257	}& \ETA{301989888} \\

@@

			& 4,1	&\cpu{ 53.08}&\wtm{9.79}&\ints{15}& \cpu{9.82}& \wtm{7.00}& \ints{21	}& \ETA{873813} \\
			& 4,2	&\cpu{117.07}&\wtm{19.09}&\ints{33}& \cpu{11.54}& \wtm{8.55}& \ints{49	}& \ETA{100663296} \\

@@

			& 2,1	&\cpu{ 70.95}&\wtm{13.45}&\ints{16}& \cpu{38.96}& \wtm{13.15}& \ints{109	}& \ETA{194} \\

@@

			& 2,2	&\cpu{ 107.28}&\wtm{17.45}&\ints{146}& \cpu{44.73}& \wtm{19.47}& \ints{281	}& \ETA{1620} \\
			& 2,3	&\cpu{ 280.05}&\wtm{38.70}&\ints{352}& \cpu{60.30}& \wtm{35.55}& \ints{718	}& \ETA{12748} \\
			& 2,4	&\cpu{ 617.94}&\wtm{81.50}&\ints{834}& \cpu{108.58}& \wtm{82.60}& \ints{1820	}& \ETA{97823} \\

@@

			& 3,1	&\cpu{1275.04}&\wtm{163.42}&\ints{771}&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}& \ETA{184984} \\
			& 3,2	&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}& \ETA{3099225} \\

@@

			& 2,2	&\cpu{488.07}&\wtm{64.77}&\ints{83}	&\cpu{81.00}&\wtm{40.30}&\ints{336}&\ETA{379982} \\

@@

			& 2,3	&\cpu{2670.87}&\wtm{330.45}&\ints{3066}	&\cpu{1331.79}&\wtm{1274.36}&\ints{13926}&\ETA{96248131} \\
			& 2,4	&\cpu{3259.37}&\wtm{436.50}&\ints{1639}&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}& \ETA{???} \\
			% TODO

@@

			& 3,1	&\cpu{222.02}&\wtm{40.04}&\ints{28}	&\cpu{69.99}&\wtm{24.25}&\ints{78}&\ETA{1572107} \\
			& 3,2	&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}&\ETA{>30m}&\ETA{>30m}&\ETA{unk.}& \ETA{???} \\
			% TODO

@@

@@

		{\bf Performance comparison.}
		Quicksand's ability to find bugs in fewer distinct interleavings %overall smaller state spaces
		does not necessarily correlate with better performance. %CPU- or even wall-clock time.
		%Comparing to the break-even point in Quicksand's evaluation \cite{quicksand},
		%most of these test configurations fall on the side favouring the single-state-space approach,
		Most of our tests are too small for its approach to pay off,
		with {\tt swapbug}(3,1) and {\tt avl\_insert}(2,3) as its notable wins.
		While the prior work showed plenty more wins \cite{quicksand},
		%an upper bound also exists:
		%in {\tt swapbug}(3,2),
		%not even the {\em minimal} state space was completed in time.
		%this suggests
		future MCs could prioritize state spaces using not just size estimation
		but state space maximality as well
		%but a hybrid approach also conisdering state space maximality and preemption bounds \cite{chess-icb},
		to soften the trade-off
		both for smaller tests and for verification.
%\end{itemize}
Speaking of which...

>>>>

			& 2,1	&\cpu{  45.78}&\wtm{9.70}&\ints{21}& \cpu{*9.47}& \wtm{*6.40}& \ints{21	}& \ETA{213} \\

@@

			& 2,2	&\cpu{  84.14}&\wtm{13.59}&\ints{*33}& \cpu{*10.39}& \wtm{*7.70}& \ints{49	}& \ETA{1536} \\
			& 2,3	&\cpu{ 131.91}&\wtm{20.44}&\ints{*73}& \cpu{*12.83}& \wtm{*9.67}& \ints{113	}& \ETA{10752} \\
			& 2,4	&\cpu{ 255.75}&\wtm{37.56}&\ints{257}& \cpu{*18.63}& \wtm{*15.86}& \ints{257	}& \ETA{73728} \\

@@

			& 3,1	&\cpu{ 114.06}&\wtm{17.45}&\ints{*15}& \cpu{*9.50}& \wtm{*6.79}& \ints{21	}& \ETA{13653} \\
			& 3,2	&\cpu{ 109.60}&\wtm{26.16}&\ints{49}& \cpu{*10.72}& \wtm{*7.97}& \ints{49	}& \ETA{393216} \\
			& 3,3	&\cpu{ 124.80}&\wtm{20.40}&\ints{*73}& \cpu{*13.84}& \wtm{*11.01}& \ints{113	}& \ETA{11010048} \\
			& 3,4	&\cpu{ 227.49}&\wtm{35.15}&\ints{*161}& \cpu{*31.37}& \wtm{*28.53}& \ints{257	}& \ETA{301989888} \\

@@

			& 4,1	&\cpu{ 53.08}&\wtm{9.79}&\ints{*15}& \cpu{*9.82}& \wtm{*7.00}& \ints{21	}& \ETA{873813} \\
			& 4,2	&\cpu{117.07}&\wtm{19.09}&\ints{*33}& \cpu{*11.54}& \wtm{*8.55}& \ints{49	}& \ETA{100663296} \\

@@

			& 2,1	&\cpu{ 70.95}&\wtm{13.45}&\ints{*16}& \cpu{*38.96}& \wtm{*13.15}& \ints{109	}& \ETA{194} \\

@@

			& 2,2	&\cpu{ 107.28}&\wtm{*17.45}&\ints{*146}& \cpu{*44.73}& \wtm{19.47}& \ints{281	}& \ETA{1620} \\
			& 2,3	&\cpu{ 280.05}&\wtm{38.70}&\ints{*352}& \cpu{*60.30}& \wtm{*35.55}& \ints{718	}& \ETA{12748} \\
			& 2,4	&\cpu{ 617.94}&\wtm{*81.50}&\ints{*834}& \cpu{*108.58}& \wtm{82.60}& \ints{1820	}& \ETA{97823} \\

@@

			& 3,1	&\cpu{*1275.04}&\wtm{*163.42}&\ints{*771}&\ETA{--}&\ETA{>30m}&\ETA{--}& \ETA{184984} \\
			& 3,2	&\ETA{--}&\ETA{>30m}&\ETA{--}&\ETA{--}&\ETA{>30m}&\ETA{--}& \ETA{3099225} \\

@@

			& 2,2	&\cpu{488.07}&\wtm{64.77}&\ints{*83}	&\cpu{*81.00}&\wtm{*40.30}&\ints{336}&\ETA{379982} \\

@@

			& 2,3	&\cpu{2670.87}&\wtm{*330.45}&\ints{*3066}&\cpu{*1331.79}&\wtm{1274.36}&\ints{13926}&\ETA{96248131} \\
			& 2,4	&\cpu{*3259.37}&\wtm{436.50}&\ints{*1639}&\ETA{--}&\ETA{>30m}&\ETA{--}& \ETA{36019973} \\
			% smaller than above? estimate's just fickle i guess; they can go up or down with time

@@

			& 3,1	&\cpu{222.02}&\wtm{40.04}&\ints{*28}	&\cpu{*69.99}&\wtm{*24.25}&\ints{78}&\ETA{1572107} \\
			& 3,2	&\cpu{*1569.09}&\wtm{*216.85}&\ints{*209}&\ETA{--}&\ETA{>30m}&\ETA{--}& \ETA{1402363529} \\

@@

		* marks the winning measurements between each series.

@@

		{\bf Performance comparison.}
		Quicksand's ability to find bugs in fewer distinct interleavings %overall smaller state spaces
		does not necessarily correlate with better performance. %CPU- or even wall-clock time.
		%Comparing to the break-even point in Quicksand's evaluation \cite{quicksand},
		%most of these test configurations fall on the side favouring the single-state-space approach,
		Most of our tests are too small for its approach to pay off,
		with {\tt swapbug}(3,1) and {\tt avl\_insert} as its notable wins.
		While the prior work showed plenty more wins \cite{quicksand},
		%an upper bound also exists:
		%in {\tt swapbug}(3,2),
		%not even the {\em minimal} state space was completed in time.
		%this suggests
		future MCs could prioritize state spaces using not just size estimation
		but state space maximality as well
		%but a hybrid approach also conisdering state space maximality and preemption bounds \cite{chess-icb},
		to soften the trade-off
		both for smaller tests and for verification.
%\end{itemize}
Speaking of which...
